\chapter{Introduction}
\label{ch:into} % This how you label a chapter and the key (e.g., ch:into) will be used to refer this chapter ``Introduction'' later in the report. 
% the key ``ch:into'' can be used with command \ref{ch:intor} to refere this Chapter.

With the rise in the digital age, the chances of online fraud have also increased significantly. Credit cards have become an integral part of financial transactions which facilitates online transactions more easily and it is also convenient for customers. However, with an increase in the use of such online transactions, there is an increase in the risk of fraud which leads to huge losses for both customers and financial institutions. Credit card fraud happens when an unidentified user makes the transaction using someone else’s card information and detecting such fraud manually is a very challenging task due to such a high number of transactions every moment. To deal with this cybercrime, an efficient fraud detection system \citep{Dornadula-2019} should be established which uses various machine learning algorithms and models to accurately detect the fraud. In this, a credit card fraud detection dataset  is taken from an online source Kaggle where the data is cleaned and processed to extract relevant information which can be used as training data for the machine learning models to accurately detect the fraud. Some machine learning algorithms \citep{Shah-2023} that are used are Logistic Regression, Decision Tree Classification, and Random forest classification which can detect fraud based on the data of past transactions and can detect fraud in real-time which is a big advantage of using machine learning algorithms. After that, these models are further tuned for provided dataset using dataset using techniques like hyperparameter tuning \citep{Dalal-2022} , which greatly enhances the model's performance. The training data used in these models are based on various factors like location, date and time of the transaction, past transactions, etc. The performance of these combined models is then evaluated using various evaluation metrics. Deployment of such fraud detection systems ensures safer transactions by improving online security.





%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Background}
\label{sec:into_back}


With the rise of digital transactions, the risk of credit card fraud has escalated. Current fraud detection systems are struggling to keep pace with evolving tactics, prompting the need for more efficient solutions. This study utilizes machine learning algorithms such as Logistic Regression and Decision Trees to craft a responsive credit card fraud detection system. Prioritizing real-time adaptability, the project seeks to enhance the security of financial transactions, contributing to the ongoing battle against credit card fraud.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Problem statement}
\label{sec:intro_prob_art}
As credit card fraud continues to rise, the limitations of traditional detection systems become clear. This research tackles the issue by using machine learning algorithms to create a more effective and adaptive solution, aiming to improve the security of financial transactions in real-time.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Aims and objectives}
\label{sec:intro_aims_obj}


\textbf{Aims:} The goal of this project is to use machine learning algorithms to create an effective credit card fraud detection system that will enhance the security for financial transactions by providing a reliable and flexible solution.




\textbf{Objectives:} First, we use machine learning methods, including Random Forest Classification, Decision Tree Classification, and Logistic Regression, to analyse historical credit card transaction data. The focus is on training the models to recognise anomalies in transaction behaviour and spotting patterns suggestive of fraudulent activity. Second, the research seeks to implement and assess the developed models in a real-time context, ensuring the system's capability to swiftly detect and mitigate potential fraud during live transactions. Additionally, the study aims to contribute to the existing knowledge in credit card fraud detection by evaluating and comparing the effectiveness of various machine learning approaches. Ultimately, the objective is to furnish financial institutions and consumers with an advanced and adaptable tool to counter the growing menace of credit card fraud, thereby fostering increased security and confidence in financial transactions.



%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Solution approach}
\label{sec:intro_sol} % label of Org section
Briefly describe the solution approach and the methodology applied in solving the set aims and objectives.

Depending on the project, you may like to alter the ``heading'' of this section. Check with you supervisor. Also, check what subsection or any other section that can be added in or removed from this template.

\subsection{A subsection 1}
\label{sec:intro_some_sub1}
You may or may not need subsections here. Depending on your project's needs, add two or more subsection(s). A section takes at least two subsections. 

\subsection{A subsection 2}
\label{sec:intro_some_sub2}
Depending on your project's needs, add more section(s) and subsection(s).

\subsubsection{A subsection 1 of a subsection}
\label{sec:intro_some_subsub1}
The command \textbackslash subsubsection\{\} creates a paragraph heading in \LaTeX.

\subsubsection{A subsection 2 of a subsection}
\label{sec:intro_some_subsub2}
Write your text here...

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Summary of contributions and achievements} %  use this section 
\label{sec:intro_sum_results} % label of summary of results
Describe clearly what you have done/created/achieved and what the major results and their implications are. 


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Organization of the report} %  use this section
\label{sec:intro_org} % label of Org section
Describe the outline of the rest of the report here. Let the reader know what to expect ahead in the report. Describe how you have organized your report. 

\textbf{Example: how to refer a chapter, section, subsection}. This report is organised into seven chapters. Chapter~\ref{ch:lit_rev} details the literature review of this project. In Section~\ref{ch:method}...  % and so on.

\textbf{Note:}  Take care of the word like ``Chapter,'' ``Section,'' ``Figure'' etc. before the \LaTeX command \textbackslash ref\{\}. Otherwise, a  sentence will be confusing. For example, In \ref{ch:lit_rev} literature review is described. In this sentence, the word ``Chapter'' is missing. Therefore, a reader would not know whether 2 is for a Chapter or a Section or a Figure.

